Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-19 article.tex
adding content to the density part

\subsection{Measurement of \acrshort{bs} density}
\noindent To make it easier to understand, and because it is related,
we will assume that solving this problem is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.

Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories :
\begin{itemize}
    \item \emph{city center};
    \item \emph{urban area};
    \item \emph{extra-urban area};
    \item \emph{courntryside}.
\end{itemize}

\subsubsection{\acrshort{dbscan}}
When thinking of density-based clustering, one of the first methods that comes in mind is probably \acrshort{dbscan}.
It is really powerful because we only have two parameters to modify.

Despite the efficiency of this method, it is not the best adapted to our problem because it's only giving us if a \acrshort{bs} is considered in a city or not.
We wanted a more continuous method.

\subsubsection{\acrshort{hdbscan}}

\subsubsection{$3$-NN mean distance}
To classify each base station we need a method.

For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{table:crit_summary}.

To make this method working properly, only \acrshort{bs} from one provider have to be kept into the calculation process.
Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, values could be modified.

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{table:crit_summary}
    \begin{tabular}{lcc}
        \toprule
        \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
        \cmidrule(lr){1-3}
        city center & $\unit[2]{km}$ & $5^\circ$ \\
        urban area & $\unit[5]{km}$ & $10^\circ$ \\
        extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

>>>>

\subsection{Measurement of \acrshort{bs} density}
\noindent Places with a high population also have a high density of base stations. In fact, each base station can only support a certain
load of users.

Therefore, we can assume that finding zones with a high density of base station is equivalent to finding the \acrshort{bs} 
situated in \og cities\fg{}.

Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories :
\begin{itemize}
    \item \emph{city center};
    \item \emph{urban area};
    \item \emph{extra-urban area};
    \item \emph{countryside}.
\end{itemize}

\subsubsection{\acrshort{dbscan}}
The goal here is to separate points that seem to belong to a denser conglomerate of base station, from the others who are a bit more spaced
to cover the countryside.

That is called density based clustering. The main method to do that is \acrshort{dbscan}.

It consists in detecting clusters based on the density, using two parameters :

\begin{itemize}
    \item \emph{$\epsilon$} : A distance threshold under which two points are considered close enough to be considered neighbours;   
    \item \emph{$n_{\text{min}}$} : The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.

\end{itemize}

The clusters will then "grow" from the core points by attaching all points close from less than \emph{$epsilon$} than a point of the said 
cluster.

Despite the efficiency of this method, it is not the best adapted to our problem because it's only giving us if a \acrshort{bs} is considered 
in a city or not, it doesn't split the points that are in a city into the four categories presented above.

\subsubsection{\acrshort{hdbscan}}
This method, introduced here \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
in selecting the best clusters after testing their persistence by making the $\epsilon$ parameter vary. It's main particularity
is that it allows to detect clusters of different densities.

To each point who belong to a cluster is associated a probability that symbolises the degree of certainty for this point to belong
to the said cluster.

This probability can be used to separate the center of the city (where the probability is very high) from the rest of the city. However,
it cannot be precise enough to separate the clusters into the four categories.

\subsubsection{$3$-NN mean distance}
For our use case, we need a more specific method. Here is the explanation of how it works:

For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
Table~\ref{table:crit_summary} (very low value for city center, slighlty higher value for urban area,\dots).

To make this method work properly, only \acrshort{bs} from one provider have to be kept into the calculation process.

Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, 
values could be modified.

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{table:crit_summary}
    \begin{tabular}{lcc}
        \toprule
        \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
        \cmidrule(lr){1-3}
        city center & $\unit[2]{km}$ & $5^\circ$ \\
        urban area & $\unit[5]{km}$ & $10^\circ$ \\
        extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        countryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}
